Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Finished 6

In the last section, we just established a computable pushdown control-flow
analysis through refunctionalization and caching. In this section,
we revisit the pushdown control-flow problem and examine what we have done to
achieve it.

\textbf{The Problem of Return-flows.}
Pushdown control-flow is a property in analysis that precisely models
the runtime call-stack of the analyzed program.
A pushdown control flow analysis provides as exact as runtime return-flow
when analyzing the program, but traditional control flow analysis collapses
the state space into a finite space thus causes imprecise stack modeling.

@@

In $k$-CFA algorithm or the abstract abstract machine we showed in section
\ref{aam},
The call sites @(id 2)@ and @(id 1)@ share the same return flow,
so the of invocation @(id 2)@ returns to both call-sites @[x (id 1)]@ and @[y (id 2)]@.
Therefore, the returned value @2@ for variable @y@ is also propagated to
variable @x@ and then imprecise analysis result is arose.
This return-flow merging is inevitable even we increase the context-sensitivity.
If we use the monovariant analysis (i.e., 0CFA), the analyzing result would be @x@ and
@y@ point to value set @{1, 2}@, because the algorithm not distinguishes
@z@ comes from different call-sites.
Under $1$-CFA, the algorithm is able to distinguish that variable @z@ of function
@id@ has two different values at two call-sites, so variable @y@
would not be polluted by @1@.
However, variable @x@ still points to value set @{1, 2}@.
Because two call-sites still share the same continuation and
it is still helplessness for separating the return-flows.

>>>>

In the previous section, we have established a computable pushdown control-flow
analysis through refunctionalization and caching. In this section,
we revisit the pushdown control flow problem and examine what we have done to
overcome it.

\textbf{The Problem with Return-flows.}
Pushdown control flow is a property in analysis that precisely models
the runtime call stack of the analyzed program.
A pushdown control flow analysis provides an as-exact-as-runtime return-flow
when analyzing a program, but traditional control flow analysis collapses
the state space into a finite space and thus causes imprecise stack modeling.

@@

In $k$-CFA algorithm or the abstract abstract machine shown in Section~\ref{aam},
the call sites @(id 2)@ and @(id 1)@ share the same return flow,
so the invocation of @(id 2)@ returns to both call-sites @[x (id 1)]@ and @[y (id 2)]@.
Therefore, the returned value @2@ for variable @y@ is also propagated to
variable @x@, causing imprecise analysis results to arise.
This return-flow merging is inevitable, even when increasing the context-sensitivity.
If we use the monovariant analysis (i.e., $0$-CFA), the analysis result would be such that @x@ and @y@ point to value set @{1, 2}@, because the algorithm does not distinguish that
@z@ comes from a different call site.
Under $1$-CFA, the algorithm is able to distinguish that variable @z@ of function
@id@ has two different values at two call sites, so variable @y@
would not be polluted by @1@.
However, variable @x@ still points to value set @{1, 2}@, because two call-sites still share the same continuation $1$-CFA is still unable to separate the return-flows.
